---
title: "Reports"
author: "Lisa DeBruine"
date: 2024-10-04
format: 
  html:
    df-print: kable
    theme: superhero
    toc: true
    toc-depth: 3
    toc-expand: true
execute:
  echo: false     # whether to show code chunks
  message: false  # whether to show messages from your code
  warning: false  # whether to show warnings from your code
  fig-width: 8    # figure width in inches (at 96 dpi)
  fig-height: 5   # figure height in inches (at 96 dpi)
---

```{r}
#| label: setup

library(tidyverse)
```

## Basic Markdown {-}

Now I can make:

* headers
* paragraphs
* lists
* [links](https://psyteachr.github.io/reprores-v6/)

1. **bold**
2. *italic*
3. ~~strikethrough~~
4. _subscript_
5. ^superscript^
6. `code`
7. [ ] task item

## Code Chunks

```{r}
# this is a code chunk
name <- "Lisa"
age <- 47
today <- Sys.Date()
halloween <- as.Date("2024-10-31")
```

My name is `r name` and I am `r age` years old. 
It is `r halloween - today` days until Halloween, 
which is my favourite holiday.

## Data Analysis

```{r}
smalldata <- read_csv("https://psyteachr.github.io/reprores/data/smalldata.csv")
```

```{r}
# count how many are in each group
group_counts <- count(smalldata, group)
```

The total number of participants in the **control** condition was `r group_counts$n[1]`. The total number of participants in the **experimental** condition was `r group_counts$n[2]`.

### Visualisation

```{r}
ggplot(data = smalldata, 
       mapping = aes(x = pre, 
                     y = post, 
                     color = group)) +
  geom_point() +
  labs(x = "Pre-test Score",
       y = "Post-test Score")
```

### Tables

All data are shown in @tbl-raw-data.

```{r}
#| label: tbl-raw-data
#| tbl-cap: The raw data from the study.
smalldata
```

